Necessity is the mother of invention

### 2017-11-01 ms.tex
fix hawaii typo; add Holsinger1986 ref

\author[a]{Yoav Ram}
\author[b]{Lee Altenberg}
\author[a]{Marcus W. Feldman}
\affil[a]{Department of Biology, Stanford University, Stanford, CA}
\affil[b]{Information and Computer Sciences, University of Hawai`I at M{\=a}noa, Honolulu, HI}

@@

The assumptions and conditions for the validity of the \emph{unified reduction principle} are~\citep{Altenberg2017}:
(i) effectively infinite population size, (ii) constant-viability selection, (iii) a population at an equilibrium, and (iv) \emph{linear variation} -- the equal scaling of transition probabilities by the modifier.
A departure from the latter assumption occurs if two variation producing processes interact~\citep{Altenberg2012} [REF: Holsinger?], or if there are biases in the mutation or migration process, such that \ldots{}

>>>>

\author[a]{Yoav Ram}
\author[b]{Lee Altenberg}
\author[a]{Marcus W. Feldman}
\affil[a]{Department of Biology, Stanford University, Stanford, CA}
\affil[b]{Information and Computer Sciences, University of Hawai`i at M{\=a}noa, Honolulu, HI}

@@

The assumptions and conditions for the validity of the \emph{unified reduction principle} are~\citep{Altenberg2017}:
(i) effectively infinite population size, (ii) constant-viability selection, (iii) a population at an equilibrium, and (iv) \emph{linear variation} -- the equal scaling of transition probabilities by the modifier.
A departure from the latter assumption occurs if two variation producing processes interact~\citep{Feldman1980,Altenberg2012}.
Departures from the \emph{reduction principle} have also been demonstrated when conditions (i)-(iii) are not met, see for example~\citet{Holsinger1986} and references therein.
